### 2018-09-27 test/report.tex
add more stuff

\subsection*{Modular hierarchy}
\subsection*{Connectivity}
\subsection*{Plasticity & synaptic resources}
\subsection*{Voltage equations}

\section*{TODO}
\begin{itemize}
\item Find papers on LIF cortical organization - how should we connect the modules? Should we do modules? What should they look like?
\end{itemize}

\cite{lippert}

>>>>

\subsection*{Modular hierarchy}
Recent models for self-organized criticality have used neural models with hundreds to thousands of tightly-connected neurons \cite{munozlg, rubinov}. We will use a similar scheme to compare with these results.\\

\subsection*{Connectivity}
\subsection*{Plasticity \& synaptic resources}
\subsection*{Voltage equations}

\section*{TODO}
\begin{itemize}
\item Find papers on LIF cortical organization - how should we connect the modules? Should we do modules? What should they look like?
\item Think about what sorts of plasticity rules would accomodate the Munoz 'synaptic resources' property - a way to make modules have propensity to do module spikes if sufficiently excited, and also a refractory period where the whole module must recover
\end{itemize}
